### 2019-03-30 stableLimit.tex
change stableLimit.tex

\subsection{Motivation and literature review}

	The study of the asymptotic behavior of the critical branching particle system has a long history.
	It is well known that for a critical Galton-Watson process $(Z_n)$, we have
	\[\label{eq: Kolmogorov's result with finite variance}
		n P(Z_n > 0)
		\xrightarrow[n\to \infty]{} \frac{2}{\sigma^2},
	\]
	and
	\[\label{eq: Yaglom's result with finite variance}
		\Big\{ \frac{Z_n}{n}; P(\cdot| Z_n > 0) \Big\}
		\xrightarrow[n \to \infty]{\operatorname{law}} \frac{\sigma^2}{2} \mathbf e,
	\]
	where $\sigma^2$ is the variance of the offspring distribution and $\mathbf e$ is an exponential random variable with mean $1$.
	The result \eqref{eq: Kolmogorov's result with finite variance} is due to Kolmogorov \cite{Kolmogorov1938Zur-losung}, and the result \eqref{eq: Yaglom's result with finite variance} is due to Yaglom \cite{Yaglom1947Certain}.
	For further references to these results, see \cite{Harris2002The-theory} and \cite{KestenNeySpitzer1966The-Galton-Watson}.
	Since then, lots of analogous results were obtained for more general critical branching processes with finite 2rd moment, see \cite{AsmussenHering1983Branching}, \cite{AthreyaNey1974Functionals}, \cite{AthreyaNey1972Branching} and \cite{JoffeSpitzer1967On-multitype} for example.

	Note that result \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are still valid even if the 2rd moment is infinite, i.e. $\sigma^2 = \infty$.
	In this case, the scaling limits in \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are degenerate, so more proper scaling is required.
	This was firstly obtained by Zolotarev \cite{Zolotarev1957More} in a simplified continuous time set-up,
	which is then extended by Slack \cite{Slack1968A-branching} for discrit time critical Galton-Watson processes allowing infinite variance:  Consider the critical Galton-Watson process $(Z_n)$ with infinite variance.
	Assuming that the offspring generating function $f(s)$ takes the form
\[\label{eq: offspring generating function with alpha moment}
	f(s)
	= s + (1-s)^{1+ \alpha} l(1-s),
	\quad s\geq 0,
\]
	where $l$ is a slowly varying function at $0$ and $0 < \alpha \leq 1$, then
\[ \label{eq: extinction probability of critical GW process without 2rd moment}
	P(Z_n > 0) = n^{-1/\alpha} L(n),
\]
	where $L$ is a slowly varying function at $\infty$, and
\[\label{eq: conditional distribution of critical GW process without 2rd moment}
	\big\{ P(Z_n > 0) Z_n; P(\cdot | Z_n > 0)\big\}
	\xrightarrow[n\to \infty]{\operatorname{law}} \mathbf z^{(\alpha)},
\]
	where $\mathbf z^{(\alpha)}$ is a positive random variable with Laplace transform
\[
	E[e^{- u \mathbf z^{(\alpha)}}]
	= 1 - (1+ u^{-\alpha})^{-1/\alpha},
	\quad u \geq 0.
\]
	In this paper, we will call the distribution of $\mathbf z^{(\alpha)}$ the \emph{Zolotarev's distribution with index $\alpha$}.
	Slack \cite{Slack1972Further} considered the converse of this problem:
	In order $\big\{ P(Z_n > 0) Z_n; P(\cdot | Z_n > 0)\big\}$ to have a non-degenerate weak limit, the offspring generating function must take the form of \eqref{eq: offspring generating function with alpha moment} for some $0 < \alpha \leq 1$.
	For shorter and more unified approaches to these results, we refer our reader to Borovkov \cite{Borovkov1989Method} and Pakes \cite{Pakes2010Critical}.

	Goldstein and Hoppe \cite{GoldsteinHoppe1978Critical} considered the asymptotic behavior of multitype critical Galton-Watson process without 2rd moment condition:
	Let $\mathbf Z_n=(Z_n^{(1)}, \dots, Z_n^{(d)})$ denote a critical, $d$-type, nonsingular and positively regular Galton-Watson process.
	Denoted by $\mathbf F(\mathbf s) = (\mathbf F^{(1)}(\mathbf s), \dots, \mathbf F^{(d)}(\mathbf s))$ the offspring probability generating function,
	%new added
	and  $\mathbf F_n(\mathbf s), \quad n>1$, its iterates.
	%end new
	Let $M$ be the mean matrix of $\mathbf Z$, $\mathbf v$ and $\mathbf u$ its left and right principle eigenvectors, respectively, corresponding to the maximal eigenvalue 1, and normalized so that $\mathbf v \cdot \mathbf u = 1$ and $\mathbf 1 \cdot \mathbf u = 1$, with $\mathbf 1$ the vector $(1,\dots, 1)$.
	Suppose that
\[\label{eq: regularly varying condition for multitype branching process}
	\mathbf v E(\mathbf 1-x\mathbf u) \mathbf u
	= x^\alpha l(x),
	\quad x > 0,
\]
	where $0 < \alpha \leq 1$; $l$ is slowly varying at $0$; and  the matrix $E(\mathbf s)$ is defined by
\[
	\mathbf 1 - \mathbf F(\mathbf s)
	= (M - E(\mathbf s))(\mathbf 1 - \mathbf s),
	\quad \mathbf s \in \mathbb R_+^d.
\]
%	Then \cite{GoldsteinHoppe1978Critical} shows that,
Then \cite{GoldsteinHoppe1978Critical} showed that,
	if we let $a_n := \mathbf v \cdot (\mathbf 1 - \mathbf F_n(\mathbf 0))$, with $\mathbf 0 \in \mathbb R_+^d$ the vector $(0,\dots, 0)$, then for each $\mathbf i \in \mathbb N_0^d \setminus \{\mathbf 0\}$,
\[ \label{eq: limit behavior of the exitinction probability without finite variance of multitype branching processes}
	n L(a_n) \operatorname{P}(\mathbf Z_n \neq \mathbf 0| Z_0 = \mathbf i)^\alpha
	\xrightarrow[n\to \infty]{} (\mathbf i \cdot \mathbf u)^\alpha / \alpha,
\]
	and for each $\mathbf j \in \mathbb N_0^d$
\[\label{eq: conditioned normalized multitype branching process}
	\{ a_n \mathbf Z_n \cdot \mathbf j ; P(\cdot | \mathbf Z_n \neq \mathbf 0, \mathbf Z_0 = \mathbf i)\}
	\xrightarrow[n\to \infty]{\operatorname{law}} (\mathbf v\cdot \mathbf j) \mathbf z^{(\alpha)}.
\]
	For the converse of this problem, Vatutin \cite{Vatutin1977Limit} showed that in order the left side of \eqref{eq: conditioned normalized multitype branching process} has a non-degenerate weak limit, one must have \eqref{eq: regularly varying condition for multitype branching process} for some $0 < \alpha \leq 1$.
	Vatutin \cite{Vatutin1977Limit} also considered analogue results for the continuous time mutitype critical Galton-Watson processes.

	Asmussen and Hering \cite{AsmussenHering1983Branching} discussed similar questions for critical branching Markov processes $(Y_t)$ in a general space $E$ under some ergodicity condition (the so-called condition (M) see \cite[p.~156]{AsmussenHering1983Branching}) on the mean semigroup of $(Y_t)$ (see \cite[Section 6.3]{AsmussenHering1983Branching} and \cite[Section 6.4]{AsmussenHering1983Branching}).
	In the case without the finite second moment, under a condition  paralleling  to \eqref{eq: regularly varying condition for multitype branching process} (the so-called condition (S) \cite[p.~207]{AsmussenHering1983Branching}), they proved results (see \cite[Theorem 4.2]{AsmussenHering1983Branching}) paralleling to \eqref{eq: limit behavior of the exitinction probability without finite variance of multitype branching processes} and \eqref{eq: conditioned normalized multitype branching process} for the critical branching Markov processes.

	The main process of interest in this article is a measure-valued Markov process with branching property known as the $(\xi, \psi)$-superprocess.
	The transition probability of such processes is determined by a Hunt process $\xi$ on a locally compact, separable, metric space $E$, and a function $\psi$ on $E \times [0,\infty)$ defined by
\[ \label{eq: branching mechanism}
	\psi(x,z):=
	- \beta(x) z + \alpha (x) z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(x,dy),
	\quad x\in E, z\geq 0,
\]
	where $\beta \in b\mathscr B_E$, $\alpha \in bp\mathscr B_E$ and $\pi(x,dy)$ is a kernel from $E$ to $(0,\infty)$ s.t. $\sup_{x\in E} \int_{(0,\infty)} (y\wedge y^2) \pi(x,dy) < \infty$.
	We refer our readers to \cite{Li2011Measure-valued} for a classical reference of superprocesses.
	$\xi$ and $\psi$ are often referred to as the spatial motion and the branching mechanism.

	Results paralleling to \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} have been obtained for some critical superprocesses by Evans and Perkins \cite{EvansPerkins1990Measure-valued} and Ren, Song and Zhang \cite{RenSongZhang2015Limit}.
	Evans and Perkins \cite{EvansPerkins1990Measure-valued} considered critical superprocesses when  the branching mechanism is $(x,z)\mapsto z^2$ and the spatial motion satisfies some ergodicity conditions.
	Ren, Song and Zhang \cite{RenSongZhang2015Limit} refined their results for a class of critical superprocesses with general branching mechanism and general spatial motions:
	Let $\{(X_t)_{t\geq 0}; \mathbf P_\mu \}$ be a critical superprocess starting from a measure $\mu$.
	Suppose that its spatial motion $\xi$ is intrinsically ultracontractive with respect to some reference measure $m$, and its branching mechanism $\psi$ satisfies the following second moment condition:
\[\label{eq: second moment condition}
	\sup_{x\in E} \int_{(0,\infty)} y^2 \pi(x,dy)
	< \infty.
\]
	Under some other mild assumptions, it was proved by Ren, Song and Zhang \cite{RenSongZhang2015Limit} that
\[\label{eq: Kolmogorov type result with 2rd moment}
	t \mathbf P_\mu(X_t \not \equiv 0)
	\xrightarrow[t\to \infty]{} c^{-1} \langle \phi, \mu \rangle_m,
\]
	and for a large class of testing functions $f$ on $E$,
\[\label{eq: Ygalom type result with 2rd moment}
	\{ t^{-1}X_t(f); \mathbf P_\mu (\cdot | X_t \not\equiv 0)\}
	\xrightarrow[t\to \infty]{\operatorname{law}} c \langle \phi^*, f\rangle_m \mathbf e.
\]
	Here, the constant $c > 0$ is independent of the choice of $\mu$ and $f$;
	$\mathbf e$ is an exponential random variable with mean $1$;
	and $\phi$ (respectively, $\phi^*$) is the principal eigenfunction of (respectively, the dual of) the generator of the mean semigroup of $X$.
	In \cite{RenSongSun2017Spine}, we also provided an alternative probabilistic approach to results \eqref{eq: Kolmogorov type result with 2rd moment} and \eqref{eq: Ygalom type result with 2rd moment}.

	As a continuation of those works, it is natural to ask weather results paralleling to \eqref{eq: extinction probability of critical GW process without 2rd moment} and \eqref{eq: conditional distribution of critical GW process without 2rd moment} can be obtained for some critical superprocesses without the second moment condition \eqref{eq: second moment condition}.
	%Perhaps a 	simpler
	A simpler
	version of this question has already been answered in the context of continuous-state branching processes (CSBP) which can be viewed as superprocesses without spatial movements.
	Kyprianou \cite{Kyprianou2008Continuous} considered a CSBP $(Y_t)$ with stable branching mechanism $\psi(z) =c z^\gamma$ where $c > 0$ and $\gamma \in (1,2]$. He showed that for all $x\geq 0$, with $c_t := (c(\gamma - 1)t)^{1/(\gamma - 1)}$,
\[ \label{eq: conditional limit of CSBP with stable branching}
	\{c_t^{-1}Y_t; P( \cdot |Y_t > 0,Y_0 = x)\}
	\xrightarrow[t\to \infty]{\operatorname{law}} \mathbf z^{(\gamma - 1)}.
\]
	Recently, Ren, Yang and Zhao \cite{RenYangZhao2014Conditional} generalized this result, by considering a CSBP with branching mechanism
\[\label{eq: regular varing of branching mechanism of a CSBP}
	\psi(z)
	= c z^\gamma l(z),
	\quad z\geq 0.
\]
	where $c > 0$, $\gamma \in (1,2]$ and $l$ is a slowly varying function at $0$.
	They showed that for all $x\geq 0$, with $\lambda_t: = P_1(Y_t > 0)$,
\[\label{eq: conditional limit of CSBP}
	\{ \lambda_t Y_t ; P(\cdot | Y_t > 0, Y_0 = x)\}
	\xrightarrow[t\to \infty]{\operatorname{law}} \mathbf z^{(\gamma - 1)}.
\]
	Later, \cite{IyerLegerPego2015Limit} considered the converse problem: Suppse that $(Z_t)$ is a CSBP with ciritical branching mechanism $\psi$
	%which verifying Grey's condition.
	which satisfies Grey's condition.
	In order the left side of  \eqref{eq: conditional limit of CSBP} has non-trivial weak limit for some positive function $(\lambda_t)$, one must have \eqref{eq: regular varing of branching mechanism of a CSBP} for some $1< \gamma \leq 2$.

	In this paper, we establish a result paralleling to \eqref{eq: conditional limit of CSBP with stable branching} for some critical $(\xi,\psi)$-superprocess $\{X; \mathbf P\}$ with spatially dependent stable branching mechanism.
	In particular, we assume that the spatial motion $\xi$ is intrinsically ultracontractive with respect to some reference measure $m$, and the branching mechanism takes the form
\[
	\psi(x,z) = -\beta (x) z + \kappa(x) z^{\gamma(x)},
	\quad x\in E, z \geq 0,
\]
	where $\beta \in b\mathscr B_E$, $\gamma \in bp\mathscr B_E$, $\kappa \in bp\mathscr B_E$ with $1< \gamma(\cdot )<2$, $\gamma_0 := \operatorname{ess\,inf}_{m(dx)} \gamma(x)> 1$ and $\operatorname{ess\,inf}_{m(dx)}\kappa(x) > 0$.
	We will show that $\mathbf P_{\delta_x}( X_t \not \equiv 0) $ convergence to $0$ while $t\to \infty$, and is regularly varying with index $\frac{1}{\gamma_0 - 1}$.
	Furthermore, if $m(x: \gamma(x) = \gamma_0)>0$, we show that
\[
	\mathbf P_{\delta_x}( X_t \not \equiv 0)
	\stackrel[t\to \infty]{}{\sim} \phi(x) \eta_t
\]
	and for a large class of non-negative testing function $f$,
\[
	\{   \eta_t X_t(f) ; \mathbf P_{\delta_x}(\cdot | X_t \not \equiv 0) \}
	\xrightarrow[t\to \infty]{\operatorname{law}}
	\langle f, \phi^*\rangle_m \mathbf z^{(\gamma_0 - 1)},
\]
	where $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} }$ and $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m$.
	A regrously statements of the assumptions and the results are presented in the next subsection.
	%Perhaps it
	It
	is interesting to mention here that, even though the stable index $\gamma(x)$ is spatially dependent, the limiting behavior of the critical superprocess $(X_t)$ is primarily depended only by the lowest index $\gamma_0$.

@@

	We first set some notations.
	For any measurable space $(E,\mathscr E)$, denote by $r\mathscr E$ the colloction of all measurable real functions on $E$.
	Define $b\mathscr E :=\{f \in r\mathscr E: \sup_{x\in E}|f(x)|<\infty \}$, $p\mathscr E :=\{f\in r\mathscr E: \forall x\in E,~f(x)\geq 0\}$ and $s\mathscr E :=\{f\in r\mathscr E: \forall x\in E,~f(x)\neq 0\}$.
	Define $bp\mathscr E := b\mathscr E \cap p\mathscr E$, $bs\mathscr E:= b\mathscr E \cap s\mathscr E$, $sp\mathscr E:= s\mathscr E \cap p\mathscr E$ and $spb\mathscr E : = s\mathscr E \cap p\mathscr E \cap b\mathscr E$.	
	Denote by $\mathcal M_E$ the collection of all measures on $(E,\mathscr E)$.
	Denote by $\mathcal M^\sigma_E$ the collection of all  $\sigma$-finite measures on $(E,\mathscr E)$.
	In this paper, to simplify the notation, we write $\mu(f)$ for the integration of a function $f$ with respect to a measure $\mu$.
%	We also write $\langle f,g\rangle_m$ meaning $ \int_E fg dm$  	if we want  to emphasize the inner product structure of Hilbert space $L^2(dm)$.
    We also write $\langle f, g\rangle_m$ for $\int_E fg dm$
    to emphasize that it is the inner product in the Hilbert space $L^2(dm)$.
	For any $\phi \in p\mathscr E$, define $\mathcal M^\phi_E:= \{\mu \in \mathcal M_E: \mu(\phi) < \infty\}$.
	In particular, $\mathcal M^1_E$ is the collection of all  finite measures on $E$.
	If $E$ is a topology space, denote by $\mathscr B_E$ the collection of all  Borel measurable subsets of $E$.

>>>>

%\subsection{Motivation and literature review}
\subsection{Background}

The study of the asymptotic behavior of 
%the critical branching particle system has a long history.
critical branching particle systems has a long history
	It is well known that for a critical Galton-Watson process $(Z_n)$, we have
	\[\label{eq: Kolmogorov's result with finite variance}
		n P(Z_n > 0)
		\xrightarrow[n\to \infty]{} \frac{2}{\sigma^2}
	\]
	and
	\[\label{eq: Yaglom's result with finite variance}
		\Big\{ \frac{Z_n}{n}; P(\cdot| Z_n > 0) \Big\}
		\xrightarrow[n \to \infty]{\operatorname{law}} \frac{\sigma^2}{2} \mathbf e,
	\]
	where $\sigma^2$ is the variance of the offspring distribution and $\mathbf e$ is an exponential random variable with mean $1$.
	The result \eqref{eq: Kolmogorov's result with finite variance} is due to Kolmogorov \cite{Kolmogorov1938Zur-losung}, and the result \eqref{eq: Yaglom's result with finite variance} is due to Yaglom \cite{Yaglom1947Certain}.
	For further references to these results, see \cite{Harris2002The-theory} and \cite{KestenNeySpitzer1966The-Galton-Watson}.
	Since then, lots of analogous results were obtained for more general critical branching processes with finite 2nd moment, see \cite{AsmussenHering1983Branching}, \cite{AthreyaNey1974Functionals}, \cite{AthreyaNey1972Branching} and \cite{JoffeSpitzer1967On-multitype} for example.

%Note that result \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are still valid even if the 2rd moment is infinite, i.e. $\sigma^2 = \infty$.
Note that \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are still valid even if the 2nd moment is infinite, i.e., $\sigma^2 = \infty$.
%In this case, the scaling limits in \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are degenerate, so more proper scaling is required.
In this case, the limits in \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are degenerate, so a more appropriate scaling is needed.
	This was first obtained by Zolotarev \cite{Zolotarev1957More} in a simplified continuous time set-up,
	which is then extended by Slack \cite{Slack1968A-branching} to discrete time critical Galton-Watson processes allowing infinite variance:  Consider a critical Galton-Watson process $(Z_n)$ with infinite variance.
	Assuming that the offspring generating function $f(s)$ is of the form
\[\label{eq: offspring generating function with alpha moment}
	f(s)
	= s + (1-s)^{1+ \alpha} l(1-s),
	\quad s\geq 0,
\]
	where $l$ is a slowly varying function at $0$ and $0 < \alpha \leq 1$, then
\[ \label{eq: extinction probability of critical GW process without 2rd moment}
	P(Z_n > 0) = n^{-1/\alpha} L(n),
\]
	where $L$ is a slowly varying function at $\infty$, and
\[\label{eq: conditional distribution of critical GW process without 2rd moment}
	\big\{ P(Z_n > 0) Z_n; P(\cdot | Z_n > 0)\big\}
	\xrightarrow[n\to \infty]{\operatorname{law}} \mathbf z^{(\alpha)},
\]
	where $\mathbf z^{(\alpha)}$ is a positive random variable with Laplace transform
\[
	E[e^{- u \mathbf z^{(\alpha)}}]
	= 1 - (1+ u^{-\alpha})^{-1/\alpha},
	\quad u \geq 0.
\]
	In this paper, we will call the distribution of $\mathbf z^{(\alpha)}$ \emph{Zolotarev's distribution with index $\alpha$}.
	Slack \cite{Slack1972Further} considered the converse of this problem:
	In order $\big\{ P(Z_n > 0) Z_n; P(\cdot | Z_n > 0)\big\}$ to have a non-degenerate weak limit, the offspring generating function must be of  the form of \eqref{eq: offspring generating function with alpha moment} for some $0 < \alpha \leq 1$.
	For shorter and more unified approaches to these results, we refer our readers to Borovkov \cite{Borovkov1989Method} and Pakes \cite{Pakes2010Critical}.

	Goldstein and Hoppe \cite{GoldsteinHoppe1978Critical} considered the asymptotic behavior of multitype critical Galton-Watson processes without the 2nd moment condition:
	Let $\mathbf Z_n=(Z_n^{(1)}, \dots, Z_n^{(d)})$ be a critical, $d$-type, nonsingular and positively regular Galton-Watson process.
	Denote by $\mathbf F(\mathbf s) = (\mathbf F^{(1)}(\mathbf s), \dots, \mathbf F^{(d)}(\mathbf s))$ the offspring probability generating function,
	and  by $\mathbf F_n(\mathbf s), \quad n>1$ its iterates. 
	Let $M$ be the mean matrix of $\mathbf Z$, $\mathbf v$ and $\mathbf u$ be its left and right principal  eigenvectors respectively, corresponding to the maximal eigenvalue 1, and normalized so that $\mathbf v \cdot \mathbf u = 1$ and $\mathbf 1 \cdot \mathbf u = 1$, with $\mathbf 1$ being the vector $(1,\dots, 1)$.
	Suppose that
\[\label{eq: regularly varying condition for multitype branching process}
	\mathbf v E(\mathbf 1-x\mathbf u) \mathbf u
	= x^\alpha l(x),
	\quad x > 0,
\]
	where $0 < \alpha \leq 1$; $l$ is slowly varying at $0$; and  the matrix $E(\mathbf s)$ is defined by
\[
	\mathbf 1 - \mathbf F(\mathbf s)
	= (M - E(\mathbf s))(\mathbf 1 - \mathbf s),
	\quad \mathbf s \in \mathbb R_+^d.
\]
Let $a_n := \mathbf v \cdot (\mathbf 1 - \mathbf F_n(\mathbf 0))$, with $\mathbf 0 \in \mathbb R_+^d$ being the vector $(0,\dots, 0)$.
It was shown in \cite{GoldsteinHoppe1978Critical} that,
 for each $\mathbf i \in \mathbb N_0^d \setminus \{\mathbf 0\}$,
\[ \label{eq: limit behavior of the exitinction probability without finite variance of multitype branching processes}
	n L(a_n) \operatorname{P}(\mathbf Z_n \neq \mathbf 0| Z_0 = \mathbf i)^\alpha
	\xrightarrow[n\to \infty]{} (\mathbf i \cdot \mathbf u)^\alpha / \alpha,
\]
	and for each $\mathbf j \in \mathbb N_0^d$
\[\label{eq: conditioned normalized multitype branching process}
	\{ a_n \mathbf Z_n \cdot \mathbf j ; P(\cdot | \mathbf Z_n \neq \mathbf 0, \mathbf Z_0 = \mathbf i)\}
	\xrightarrow[n\to \infty]{\operatorname{law}} (\mathbf v\cdot \mathbf j) \mathbf z^{(\alpha)}.
\]
	For the converse of this problem, Vatutin \cite{Vatutin1977Limit} showed that in order for the left side of \eqref{eq: conditioned normalized multitype branching process} has a non-degenerate weak limit, one must have \eqref{eq: regularly varying condition for multitype branching process} for some $0 < \alpha \leq 1$.
	Vatutin \cite{Vatutin1977Limit} also considered analogous results for the continuous time mutitype critical Galton-Watson processes.

	Asmussen and Hering \cite{AsmussenHering1983Branching} discussed similar questions for critical branching Markov processes $(Y_t)$ in a general space $E$ under some ergodicity condition (the so-called condition (M), see \cite[p.~156]{AsmussenHering1983Branching}) on the mean semigroup of $(Y_t)$ (see \cite[Section 6.3]{AsmussenHering1983Branching} and \cite[Section 6.4]{AsmussenHering1983Branching}).
	When the second moment is infinite, under a condition  parallel  to \eqref{eq: regularly varying condition for multitype branching process} (the so-called condition (S) \cite[p.~207]{AsmussenHering1983Branching}), results parallel to \eqref{eq: limit behavior of the exitinction probability without finite variance of multitype branching processes} and \eqref{eq: conditioned normalized multitype branching process} were proved in \cite{AsmussenHering1983Branching} for critical branching Markov processes,
see \cite[Theorem 4.2]{AsmussenHering1983Branching}.

%	The main process of interest in this article is a measure-valued Markov process with branching property known as the $(\xi, \psi)$-superprocess.
%	The transition probability of such processes is determined by a Hunt process $\xi$ on a locally compact, separable, metric space $E$, and a function $\psi$ on $E \times [0,\infty)$ defined by
In this paper, we are interested in a class of measure-valued branching Markov process 
known as $(\xi, \psi)$-superprocesses.
$\xi$, the spatial motion of the superprocess, is a a Hunt process on a locally 
compact, separable, metric space $E$, $\psi$, the branching mechanism of the superprocess,
is function $\psi$ on $E \times [0,\infty)$ of the form
\[ \label{eq: branching mechanism}
	\psi(x,z):=
	- \beta(x) z + \alpha (x) z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(x,dy),
	\quad x\in E, z\geq 0,
\]
	where $\beta \in \mathscr B_b(E)$, $\alpha \in \mathscr B^+_b(E)$ and $\pi(x,dy)$ is a kernel from $E$ to $(0,\infty)$ such that $\sup_{x\in E} \int_{(0,\infty)} (y\wedge y^2) \pi(x,dy) < \infty$.
	For the precise definition and properties of superprocesses, see \cite{Li2011Measure-valued}.
	In the next subsection, we will give a more precise description of $(\xi, \psi)$-superprocesses.
%	We refer our readers to \cite{Li2011Measure-valued} for a classical reference of superprocesses.
%	$\xi$ and $\psi$ are often referred to as the spatial motion and the branching mechanism.

	Results parallel to \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} have been obtained for some critical superprocesses by Evans and Perkins \cite{EvansPerkins1990Measure-valued} and Ren, Song and Zhang \cite{RenSongZhang2015Limit}.
	Evans and Perkins \cite{EvansPerkins1990Measure-valued} considered critical superprocesses with branching mechanism of the form $(x,z)\mapsto z^2$ and with the spatial motion satisfying some ergodicity conditions.
	Ren, Song and Zhang \cite{RenSongZhang2015Limit} extended the results of \cite{EvansPerkins1990Measure-valued} to  
	a class of critical superprocesses with general branching mechanism and general spatial motions:
	Let $\{(X_t)_{t\geq 0}; \mathbf P_\mu \}$ be a critical superprocess starting from a measure $\mu$.
	Suppose the spatial motion $\xi$ is intrinsically ultracontractive with respect to some reference measure $m$ and the branching mechanism $\psi$ satisfies the following second moment condition:
\[\label{eq: second moment condition}
	\sup_{x\in E} \int_{(0,\infty)} y^2 \pi(x,dy)
	< \infty.
\]
	Under some other mild assumptions, it was proved in  \cite{RenSongZhang2015Limit} that
\[\label{eq: Kolmogorov type result with 2rd moment}
	t \mathbf P_\mu(X_t \not \equiv 0)
	\xrightarrow[t\to \infty]{} c^{-1} \langle \phi, \mu \rangle_m,
\]
	and for a large class of testing functions $f$ on $E$,
\[\label{eq: Ygalom type result with 2rd moment}
	\{ t^{-1}X_t(f); \mathbf P_\mu (\cdot | X_t \not\equiv 0)\}
	\xrightarrow[t\to \infty]{\operatorname{law}} c \langle \phi^*, f\rangle_m \mathbf e.
\]
	Here, the constant $c > 0$ is independent of the choice of $\mu$ and $f$;
	$\mathbf e$ is an exponential random variable with mean $1$;
	and $\phi$ (respectively, $\phi^*$) is the principal eigenfunction of (respectively, the dual of) the generator of the mean semigroup of $X$.
	In \cite{RenSongSun2017Spine}, we also provided an alternative probabilistic approach to\eqref{eq: Kolmogorov type result with 2rd moment} and \eqref{eq: Ygalom type result with 2rd moment}.

	It is natural to ask whether results parallel to \eqref{eq: extinction probability of critical GW process without 2rd moment} and \eqref{eq: conditional distribution of critical GW process without 2rd moment} are still valid for some critical superprocesses without the second moment condition \eqref{eq: second moment condition}.
	A simpler
	version of this question has already been answered in the context of continuous-state branching processes (CSBP) which can be viewed as superprocesses without spatial movements.
	Kyprianou \cite{Kyprianou2008Continuous} considered CSBP's $(Y_t)$ with stable branching mechanism $\psi(z) =c z^\gamma$ where $c > 0$ and $\gamma \in (1,2]$. He showed that for all $x\geq 0$, with $c_t := (c(\gamma - 1)t)^{1/(\gamma - 1)}$,
\[ \label{eq: conditional limit of CSBP with stable branching}
	\{c_t^{-1}Y_t; P( \cdot |Y_t > 0,Y_0 = x)\}
	\xrightarrow[t\to \infty]{\operatorname{law}} \mathbf z^{(\gamma - 1)}.
\]
	Recently, Ren, Yang and Zhao \cite{RenYangZhao2014Conditional} studied CSBP's with branching mechanism
\[\label{eq: regular varing of branching mechanism of a CSBP}
	\psi(z)
	= c z^\gamma l(z),
	\quad z\geq 0.
\]
	where $c > 0$, $\gamma \in (1,2]$ and $l$ is a slowly varying function at $0$.
It was proved in  \cite{RenYangZhao2014Conditional} that for all $x\geq 0$, with $\lambda_t: = P_1(Y_t > 0)$,
\[\label{eq: conditional limit of CSBP}
	\{ \lambda_t Y_t ; P(\cdot | Y_t > 0, Y_0 = x)\}
	\xrightarrow[t\to \infty]{\operatorname{law}} \mathbf z^{(\gamma - 1)}.
\]
	Later, Iyer, Leger and Pego \cite{IyerLegerPego2015Limit} considered the converse problem: Suppse that $(Z_t)$ is a CSBP with ciritical branching mechanism $\psi$ 
	satisfying Grey's condition.
	In order for the left side of  \eqref{eq: conditional limit of CSBP} has non-trivial weak limit for some positive function $(\lambda_t)$, one must have \eqref{eq: regular varing of branching mechanism of a CSBP} for some $1< \gamma \leq 2$.

%	In this paper, we establish a result paralleling 
In this paper, we will establish a result parallel
	to \eqref{eq: conditional limit of CSBP with stable branching} for some 
   critical $(\xi,\psi)$-superprocess $\{X; \mathbf P\}$ 
	with spatially dependent stable branching mechanism.
	In particular, we assume that the spatial motion $\xi$ is intrinsically ultracontractive with respect to some reference measure $m$, and the branching mechanism takes the form
\[
	\psi(x,z) = -\beta (x) z + \kappa(x) z^{\gamma(x)},
	\quad x\in E, z \geq 0,
\]
	where $\beta \in \mathscr B_b(E)$, $\gamma \in \mathscr B^+_b(E)$, $\kappa \in \mathscr B^+_b(E)$ with $1< \gamma(\cdot )<2$, $\gamma_0 := \operatorname{ess\,inf}_{m(dx)} \gamma(x)> 1$ and $\operatorname{ess\,inf}_{m(dx)}\kappa(x) > 0$.
	We will show that $\mathbf P_{\delta_x}( X_t \not \equiv 0) $ converges to $0$ as $t\to \infty$ and is regularly varying with index $\frac{1}{\gamma_0 - 1}$ at $\infty$..
	Furthermore, if $m(x: \gamma(x) = \gamma_0)>0$, we show that
\[
	\mathbf P_{\delta_x}( X_t \not \equiv 0)
	\stackrel[t\to \infty]{}{\sim} \phi(x) \eta_t
\]
	and for a large class of non-negative testing functions $f$,
\[
	\{   \eta_t X_t(f) ; \mathbf P_{\delta_x}(\cdot | X_t \not \equiv 0) \}
	\xrightarrow[t\to \infty]{\operatorname{law}}
	\langle f, \phi^*\rangle_m \mathbf z^{(\gamma_0 - 1)},
\]
	where $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} }$ and $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m$.
	Precise statements of the assumptions and the results are presented in the next subsection.
It is interesting to mention here that, even though the stable index $\gamma(x)$ is spatially dependent, the limiting behavior of the critical superprocess $(X_t)$ depend primarily on the lowest index $\gamma_0$.

@@

	We first fix our notation.
	For any measurable space $(E,\mathscr E)$, we denote by $\mathscr E$ the collection of all real-valued measurable functions on $E$.
	Define $\mathscr E_b :=\{f \in \mathscr E: \sup_{x\in E}|f(x)|<\infty \}$, $\mathscr E^+ :=\{f\in \mathscr E: \forall x\in E,~f(x)\geq 0\}$ and $\mathscr E^{++} :=\{f\in \mathscr E: \forall x\in E,~f(x)> 0\}$.
	Define $\mathscr E^+_b := \mathscr E_b \cap \mathscr E^+$, $\mathscr E^{++}_b:= \mathscr E_b \cap \mathscr E^{++}$.	
	Denote by $\mathcal M_E$ the collection of all measures on $(E,\mathscr E)$.
	Denote by $\mathcal M^\sigma_E$ the collection of all  $\sigma$-finite measures on $(E,\mathscr E)$.
	For simplicity, we write $\mu(f)$ for the integration of a function $f$ with respect to a measure $\mu$.
    We also write $\langle f, g\rangle_m$ for $\int_E fg dm$  
    to emphasize that it is the inner product in the Hilbert space $L^2(dm)$.
	For any $\phi \in \mathscr E^+$, define $\mathcal M^\phi_E:= \{\mu \in \mathcal M_E: \mu(\phi) < \infty\}$.
	In particular, $\mathcal M^1_E$ is the collection of all  finite measures on $E$.
	If $E$ is a topological space, denote by $\mathscr B(E)$ the collection of all  Borel subsets of $E$.
